Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2016-04-23 tese2/evaluation.tex
[ADD] optimal ratio confidence intervals
[RFT] using gnuplot

\begin{figure}[!htb]
  \begin{center}
    \input{stats/test_full_features_net.tex}
  \end{center}
  \caption{Network usage after implementing all features}
  \label{fig:test_full_features_net}
\end{figure}

@@

\begin{figure}[!htb]
  \begin{center}
    \input{stats/summary_full_net.tex}
  \end{center}
  \caption{Average network usage per interval of events after implementing all features}
  \label{fig:summary_full_net}
\end{figure}

@@

  \begin{figure}[!htb]
  \begin{center}
    \input{stats/test_client_net.tex}
  \end{center}
  \caption{Client Network usage during our test case}
  \label{fig:test_client_net}
\end{figure}

@@

\begin{figure}[!htb]
  \begin{center}
    \input{stats/test_full_features_mem.tex}
  \end{center}
  \caption{Memory usage after implementing all features}
  \label{fig:test_full_features_mem}
\end{figure}

@@

\begin{figure}[!htb]
  \begin{center}
    \input{stats/test_ram_fixed_mem.tex}
  \end{center}
  \caption{Memory usage after fixing recorder memory leak}
  \label{fig:test_ram_fixed_mem}
\end{figure}

@@

\begin{figure}[!htb]
  \begin{center}
    \input{stats/test_full_features_cpu.tex}
  \end{center}
  \caption{Percentage of CPU used during the performance tests}
  \label{fig:test_full_features_cpu}
\end{figure}

@@

\begin{figure}[!htb]
  \begin{center}
    \input{stats/test_full_features_cpu_zoom.tex}
  \end{center}
  \caption{Percentage of CPU used during the performance tests}
  \label{fig:test_full_features_cpu_zoom}
\end{figure}

@@

\begin{figure}[!htb]
  \begin{center}
    \input{stats/summary_full_cpu.tex}
  \end{center}
  \caption{Average percentage of CPU used per interval of events after implementing all features (zoomed)}
  \label{fig:summary_full_cpu}
\end{figure}

@@

  \begin{figure}[!htb]
  \begin{center}
    \input{stats/test_without_qrcode_cpu.tex}
  \end{center}
  \caption{Percentage of CPU used during the performance tests without QR code detection}
  \label{fig:test_without_qrcode_cpu}
\end{figure}

@@

  \begin{figure}[!htb]
  \begin{center}
    \input{stats/test_two_times_cpu.tex}
  \end{center}
  \caption{Percentage of CPU used during two consecutive test cases}
  \label{fig:test_two_times_cpu}
\end{figure}

@@

\begin{figure}[!htb]
  \begin{center}
    \input{stats/test_two_times_mem.tex}
  \end{center}
  \caption{Memory usage during two consecutive test cases}
  \label{fig:test_two_times_mem}
\end{figure}

@@

  \begin{figure}[!htb]
  \begin{center}
    \input{stats/test_hour_mem.tex}
  \end{center}
  \caption{Memory usage during one hour with seven clients}
  \label{fig:test_hour_mem}
\end{figure}

@@

>>>>

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{stats/test_full_features_net.eps}
  \caption{Network usage after implementing all features}
  \label{fig:test_full_features_net}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{stats/summary_full_net.eps}
  \caption{Average network usage per interval of events after implementing all features}
  \label{fig:summary_full_net}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{stats/test_client_net.eps}
  \caption{Client Network usage during our test case}
  \label{fig:test_client_net}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{stats/test_full_features_mem.eps}
  \caption{Memory usage after implementing all features}
  \label{fig:test_full_features_mem}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{stats/test_ram_fixed_mem.eps}
  \caption{Memory usage after fixing recorder memory leak}
  \label{fig:test_ram_fixed_mem}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{stats/test_full_features_cpu.eps}
  \caption{Percentage of CPU used during the performance tests}
  \label{fig:test_full_features_cpu}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{stats/test_full_features_cpu_zoom.eps}
  \caption{Percentage of CPU used during the performance tests (zoomed)}
  \label{fig:test_full_features_cpu_zoom}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{stats/summary_full_cpu.eps}
  \caption{Average percentage of CPU used per interval of events after implementing all features}
  \label{fig:summary_full_cpu}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{stats/test_without_qrcode_cpu.eps}
  \caption{Percentage of CPU used during the performance tests without QR code detection}
  \label{fig:test_without_qrcode_cpu}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{stats/test_two_times_cpu.eps}
  \caption{Percentage of CPU used during two consecutive test cases}
  \label{fig:test_two_times_cpu}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{stats/test_two_times_mem.eps}
  \caption{Memory usage during two consecutive test cases}
  \label{fig:test_two_times_mem}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{stats/test_hour_mem.eps}
  \caption{Memory usage during one hour with seven clients}
  \label{fig:test_hour_mem}
\end{figure}

@@

In order to measure the users learning speed, we have performed tests with experienced users in order to retrieve the optimal task duration and minimal task clicks.

To this end, with regard to optimal task duration and minimal clicks, we obtained the values shown in table \ref{table:optimal}.

\begin{table}[H]
\centering
\caption{Metrics for an experienced user}
\label{table:optimal}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\textbf{Task} & 1 & 2 & 3 & 4 & 5 \\ \hline
\textbf{Time} & 20 & 35 & 30 & 25 & 35 \\ \hline
\textbf{Clicks} & 7 & 10 & 5 & 9 & 7 \\ \hline
\end{tabular}
\end{table}

### 2016-04-23 tese2/stats/user_evals.tex
[RFT] using gnuplot

\begin{tikzpicture}[scale=1.0],
\centering
\begin{axis}[
height=6cm,
width=14cm,  
  ymax=100,
  ymin=0,
  xmin=0.5,
  xmax=10.5,
  axis y line*=left,
  axis x line*=bottom,
  xticklabels={Sound quality,Video quality,Layout organization,Content editor,Collaborative editor,Time navigation, Annotation handling, Content search,Member management,Chat},
  xtick={1,...,10},
  ytick={0,20,...,200},
      ymajorgrids=true,
      xmajorgrids=true,
      grid style=dashed,
  x tick label style={rotate=45,anchor=east}]
\addplot+[only marks][error bars/.cd,y dir=both, y explicit]
coordinates {
(1,69) +- (8,8)
(2,50) +- (7,7)
(3,58) +- (11,11)
(4,54) +- (12,12)
(5,64) +- (12,12)
(6,75) +- (8,8)
(7,67) +- (8,8)
(8,66) +- (10,10)
(9,80) +- (8,8)
(10,78) +-(8,8)
};
\addplot[dashed] coordinates {(0,0) (5.5,0)};
\end{axis}
\end{tikzpicture}%

>>>>

\begin{tikzpicture}[scale=1.0],
\centering
\begin{axis}[
height=6cm,
width=14cm,  
  xlabel={Questions},
  ylabel={User evaluation},
  ymax=100,
  ymin=0,
  xmin=0.5,
  xmax=10.5,
  axis y line*=left,
  axis x line*=bottom,
  xticklabels={Sound quality,Video quality,Layout organization,Content editor,Collaborative editor,Time navigation, Annotation handling, Content search,Member management,Chat},
  xtick={1,...,10},
  ytick={0,20,...,200},
      ymajorgrids=true,
      xmajorgrids=true,
      grid style=dashed,
  x tick label style={rotate=45,anchor=east}]
\addplot+[only marks][error bars/.cd,y dir=both, y explicit]
coordinates {
(1,69) +- (8,8)
(2,50) +- (7,7)
(3,58) +- (11,11)
(4,54) +- (12,12)
(5,64) +- (12,12)
(6,75) +- (8,8)
(7,67) +- (8,8)
(8,66) +- (10,10)
(9,80) +- (8,8)
(10,78) +-(8,8)
};
\addplot[dashed] coordinates {(0,0) (5.5,0)};
\end{axis}
\end{tikzpicture}%

### 2016-04-23 tese2/stats/user_times.tex
[RFT] using gnuplot

\begin{tikzpicture}[scale=1.0],
\centering
\begin{axis}[
height=6cm,
width=7cm,  
  ymax=150,
  ymin=0,
  xmin=0.5,
  xmax=5.5,
  axis y line*=left,
  axis x line*=bottom,
  xticklabels={Task 1,Task 2,Task 3,Task 4,Task 5},
  xtick={1,...,5},
  ytick={0,20,...,200},
        ymajorgrids=true,
      xmajorgrids=true,
      grid style=dashed,
  x tick label style={rotate=45,anchor=east}]
\addplot+[only marks][error bars/.cd,y dir=both, y explicit]
coordinates {
(1,57.7) +- (12.827,12.827)
(2,120.44) +- (16.041,16.041)
(3,80.409) +- (15.067,15.067)
(4,99.91) +- (11.948,11.948)
(5,117.92) +- (16.31,16.31)
};
\addplot[dashed] coordinates {(0,0) (5.5,0)};
\end{axis}
\end{tikzpicture}%

>>>>

\begin{tikzpicture}[scale=1.0],
\centering
\begin{axis}[
height=6cm,
width=7cm,  
  xlabel={Tasks},
  ylabel={Duration (seconds)},
  ymax=150,
  ymin=0,
  xmin=0.5,
  xmax=5.5,
  axis y line*=left,
  axis x line*=bottom,
  xticklabels={Task 1,Task 2,Task 3,Task 4,Task 5},
  xtick={1,...,5},
  ytick={0,20,...,200},
        ymajorgrids=true,
      xmajorgrids=true,
      grid style=dashed,
  x tick label style={rotate=45,anchor=east}]
\addplot+[only marks][error bars/.cd,y dir=both, y explicit]
coordinates {
(1,57.7) +- (12.827,12.827)
(2,120.44) +- (16.041,16.041)
(3,80.409) +- (15.067,15.067)
(4,99.91) +- (11.948,11.948)
(5,117.92) +- (16.31,16.31)
};
\addplot[dashed] coordinates {(0,0) (5.5,0)};
\addplot[only marks,mark=*,mark options={}] coordinates {
(1,20) (2,35) (3,30) (4,25) (5,35)
};

\end{axis}
\end{tikzpicture}%
